Exception Handling Bug Hazards in Android

### 2015-09-29 SPRINGER_JOURNAL/msr_journal.tex
table prevent

 In previous work~\cite{coelhoetal15}, we mined exception stack traces available on issues reported on several Android projects hosted in GitHub and Googlecode. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard the toy-programs and non-Android repositories. For each repository, we extract the developers whose email are registered on each repository. We emailed the developers and received 74 answers.

@@

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Top Resons} & \bfseries{\#} & \bfseries{\%} \\
\hline
\bfseries{For Positively Affecting Robustness} &   &   \\
Exception message improves error diagnosis &	10	& 14\% \\
Anticipated erroneous situation help writing more robust code & 9	 & 13\% \\
Exceptions for unrecoverable behavior	& 7 &	10\% \\
Checked exceptions force handling  &	6	& 9\% \\
Useful to gracefully crash 	& 4 &	6\% \\

@@

>>>>

 In previous work~\cite{coelhoetal15}, we mined exception stack traces available on issues reported on several Android projects hosted in GitHub and Googlecode. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard the toy-programs and non-Android repositories. For each repository, we extract the developers whose email are registered on each repository. We emailed the developers and received 68 valid answers.

@@

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Top Resons} & \bfseries{\#} & \bfseries{\%} \\
\hline
\bfseries{For Positively Affecting Robustness} &   &   \\
Exception message improves error diagnosis &	10	& 15\% \\
Anticipated erroneous situation help writing more robust code & 9	 & 13\% \\
Exceptions for unrecoverable behavior	& 7 &	10\% \\
Checked exceptions force handling  &	6	& 9\% \\
Useful to gracefully crash 	& 4 &	6\% \\

@@

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Top Ways} & \bfseries{\#} & \bfseries{\%} \\
\hline
Handling exceptions & 18 & 25\% \\
       - handling exceptions in all entry points/all over	  &   &   \\	
       - using catch-all clauses 		  &   &   \\	
       - addinf try catch bocks around risky methods		  &   &   \\	
Crash report tools	& 6 &	8\% \\
Null checks &	11	& 15\% \\
 - null check annotations (@Null and @NonNull)	& 3 & 	4\% \\
Edge cases/boundaries checks  &	4 &	6\% \\
Testing &	15 &	21\% \\

Let it crash and fix afterward	& 4 & 6\% \\

Many device specific exceptions prevent proper handling	& 1 & 1\% \\

\hline
\end{tabular}
\caption{Top ways of preventing crashes }
\label{tab:topreasons}
\end{table}
